Factors determining how catchments respond to forest cover change. Re-analysing global data sets.

### 2022-02-02 paper/Forest_and_Water/Forest_and_Water.Rmd
Update Forest_and_Water.Rmd
Figure 2 label corrected
Figure 4 modified with new data and all catchments

This shows that for the data related to forest decreases, there is almost always a positive flow change. In other words, flow almost always increased. However, for increases in forest cover, this is not the case, and flow can both increase and decrease. However in both cases the variability in the reported change in flow increases with the increase in forest cover change.

@@

include_graphics("../../data/FAOET0data.png")
```

>>>>

In addition, Figure 2 shows that for the data related to forest decreases, there is almost always a positive flow change. In other words, flow almost always increased. However, for increases in forest cover, this is not the case, and flow can both increase and decrease. However in both cases the variability in the reported change in flow increases with the increase in forest cover change.

@@

include_graphics("../../data/FAOET0data_final_2022.png")
```
